{\setstretch{1.5}

\section*{Completions Requirements (Bangkit Welcome Kit)}

Careful planning has gone into designing the curriculum for this program from beginning to end. At the conclusion of the program, all participants who meet the completion criteria, will be regarded as Bangkit Graduates and given certificate of accomplishment/completion and a complete transcript. Those who didn’t complete all the Bangkit will get Certificate of Attendance and partial transcript. Bangkit Graduates will also receive a voucher for the certification exam of their respective Learning Path. The requirements for graduation from Bangkit 2022 are as follows:


\begin{itemize}
    \item \textbf{Attending and actively participating in mandatory sessions,} including but not limited to:
        \begin{itemize}
            \item Bangkit 2022 Opening Session
            \item 80\% of the Instructor-led sessions for Tech* 
            \item 80\% of the Instructor-led sessions for Soft Skills*
            \item 90\% of mandatory guest/special lectures*
        \end{itemize}
    \item[] \textbf{Sessions will be informed at least 7 calendar days before. So please check your calendar on a daily basis}
    \item \textbf{For self-paced sessions, you just need to complete them in the same week.}
    \item[]If you have things to do for the allocated self-paced time, you don’t need to fill the form. Just allocate another time outside Bangkit allocated time to study and adjust by yourself. As you’re aware, the Bangkit learning method combines online self-paced study, online synchronous / instructor-led training (ILT), and project-based learning. Therefore, to help you plan your time, we have created a Bangkit learning schedule.
    \item \textbf{Submit your own work for assignments and projects.}
    \item[] Bangkit is part of the Kampus Merdeka program where academic honesty is upheld. You should demonstrate and uphold the highest integrity and honesty in all the academic work that you do. Plagiarism isn’t permitted and score for the respective assignment will be void/canceled in the event your work is flagged for plagiarism. Our learning platform partners may ban or disable your account if you plagiarize or are dishonest based on their sole discretion.
    \item \textbf{Completing official Bangkit assignments} (including classroom and our learning platform partners - Dicoding, Google Cloud Skills Boost, Coursera) each in accordance with their respective standards. Late submission will be accepted, but will reduce the respective assignment score.
    \item \textbf{Contributing to Bangkit Capstone Project.}
    \item[] This will be scored by the Bangkit Committee and your team members and includes your attendance in the final project presentation. 
    \item \textbf{Adhering to the Bangkit Code of Conduct}
\end{itemize}
}
